---
title: "lecture_note_linear_regression"
author: "Qingyue Zhuo qz2493"
date: "2022-11-27"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
set.seed(1)
```

### model fitting
The code below loads and cleans the Airbnb data
```{r}
data("nyc_airbnb")

nyc_airbnb =
  nyc_airbnb %>%
  mutate(stars = review_scores_location/2) %>%
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood
  ) %>%
  filter(borough != "Staten Island") %>%
  select(price, stars, borough, neighborhood, room_type)
```

let's fit a model: the price is an outcome that may depend on rating and borough, interactions between variables can be specified using *.  An intercept model: outcome ~ 1 +...，a model with no intercept: outcome ~ 0 +..., a model using all available predictors: outcome ~. 
```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

R will treat categorical covariates appropriately: indicators are created for non-reference category and included in your model, and factor level is treated as the reference, changing reference categories won't change "fit" or statistical significance but can affect ease of intepretation
```{r}
nyc_airbnb =
  nyc_airbnb %>%
  mutate(
    borough = fct_infreq(borough), # reorder factor levels by first appearance, frequency or numeric orders
    room_type = fct_infreq(room_type)
  )

fit = lm(price ~ stars + borough, data = nyc_airbnb)
```

### tidying output
none of the followings are tidy
```{r}
summary(fit) # an object of class summary.lm- a list
summary(fit)$coef # a vector of cofficient values
coef(fit)
fitted.values(fit)
```

```{r}
fit %>%
  broom::glance()
```

```{r}
fit %>%
  broom::tidy() %>%
  select(term, estimate, p.value) %>%
  mutate(term = str_replace(term, "borough", "Borough:")) %>% #replace matched terms with strings
  knitr::kable(digits = 3)
```


### Diagnositc
Regression diagnostics can identify issues in model fit, especially related to certain failures in model assumptions. Examining residuals and fitted values are therefore an important component of any modeling exercise.
The modelr package can be used to add residuals and fitted values to a dataframe.
```{r}
modelr::add_residuals(nyc_airbnb, fit)
```

```{r}
modelr::add_predictions(nyc_airbnb, fit)
```

```{r}
nyc_airbnb %>%
  modelr::add_residuals(fit) %>%
  ggplot(aes(x = borough, y = resid)) + geom_violin()
```

```{r}
nyc_airbnb %>%
  modelr::add_residuals(fit) %>%
  ggplot(aes(x = stars, y = resid)) + geom_point()
```
Based on the image, most notably issue is the presence of extremely outliers in price and a generally skewed residual distribution. There are a few things we might try to do here: creating a formal rule for exclusion of outliers, transforming the price variable, or fitting a model that is robust to outliers. Dealing with these issues isn't really the purpose of this class.

### Hypothesis Testing
Model summaries include results of t-test for single coefficients, and are the stardard way of assessing statistical significance.
A useful way to test multiple coefficients is to use nested models, meaning that the terms in a simple null model are a subset of the terms in a more complex alternative model.

```{r}
fit_null = lm(price ~stars + borough, data = nyc_airbnb)
fit_alt = lm(price ~stars + borough + room_type, data = nyc_airbnb)
```

```{r}
anova(fit_null, fit_alt) %>%
  broom::tidy()
```


### Nesting data
Let's fit models to datasets nested within variables - meaning, essentially, that we'll use nest to create a list column containing datasets and fit separate model to each. This is very difference from fitting nested models.
```{r}
nyc_airbnb %>%
  lm(price ~ stars * borough + room_type * borough, data = .) %>%
  broom::tidy() %>%
  knitr::kable(digit = 3)
```

alternatively, we can nest within boroughs and fit borough-specific models associating price with rating and room type:
```{r}
nest_lm_res =
  nyc_airbnb %>%
  nest(data = -borough) %>%
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>%
  select(-data, -models) %>%
  unnest(results)
  
```

```{r}
nest_lm_res %>%
  select(borough, term, estimate) %>%
  mutate(term = fct_inorder(term)) %>%
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>%
  knitr::kable(digits = 3)
```

```{r}
manhattan_airbnb = 
  nyc_airbnb %>%
  filter(borough == "Manhattan")

manhattan_nest_lm_res = 
  manhattan_airbnb %>%
  nest(data = -neighborhood) %>%
  mutate(
    models = map(data, ~lm(price ~ stars +room_type, data = .x)),
    results = map(models, broom::tidy)) %>%
  select(-data, -models) %>%
  unnest(results)
```

add the chunk below shows the neighorhood-specific estimates for the coefficients related to room type
```{r}
manhattan_nest_lm_res %>%
  filter(str_detect(term, "room_type")) %>% # detect the presence or absence of an subject
  ggplot(aes(x = neighborhood, y = estimate))+
  geom_point() +
  facet_wrap(~term)+
  theme(axis.text = element_text(angle = 80, hjust = 1))
```

